A planetary collision afterglow and transit of the resultant debris cloud

### 2023-11-09 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
\begin{centering}
\includegraphics[width=\textwidth]{figures/all_phot_nature_delta_flux.pdf}
\caption{\textbf{Optical and infrared photometry of ASASSN-21qj.}
%
{\bf a}, Normalized optical photometry from ASAS-SN in the $V$-band and the $g'$ band.
%
{\bf b},Fractional flux increase in brightness of ASASSN-21qj in both the $W1$ and $W2$ bands, for which a value of 1.0 represents the stellar contribution alone.
%
{\bf c},Calculated NEOWISE color temperature estimated from the photometry of the two bands.
%
The color temperature is plotted as zero when there is no infrared excess and is consistent with a temperature of 1000\,K while the excess is present.
%
Error bars are shown at $1\sigma$ confidence.
}
\label{fig:wisephot}
\script{plot_all_phot_nature_delta_flux.py}
\end{centering}
\end{figure}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_simple.pdf}
      \caption{\textbf{The light curve of ASASSN-21qj from several different photometric surveys and the derived transverse velocities.}
      %
      {\bf a},The eclipse depth is deeper for shorter wavelengths, indicating that the transiting material is dominated by sub-micron sized grains.
      %
      {\bf b},Transverse velocities derived from the light-curve gradients.
      %
      These are lower limits to the true velocity, and thus imply that the transiting material is closer to the star than 16\,au.
      %
      Error bars are shown at $1\sigma$ confidence.
      }
        \label{fig:eclipse_overview}
\script{plot_master_lightcurve_nature_simple.py}
\end{centering}
\end{figure*}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=\columnwidth]{figures/Size_cooling_combined_figure.pdf}
\caption{\textbf{The size and temporal evolution of a post-impact body.}
%
A post-impact body of a few to tens of Earth masses could be large enough to explain the observed increase in thermal emission from ASASSN-21qj and the subsequent infrared fluxes.
%
{\bf a},The Hill radii for bodies at different semi-major axes (solid colored lines) and the Bondi radii (dashed lines) assuming different compositions for the vapor of the post-impact body.
%
The horizontal black dashed line shows the radius required to explain the observed flux at the inferred emission temperature of 1000~K. 
%
%{\bf b,c},The change in excess flux owing to a post-impact body with time for a simple model of cooling of a post-impact body for different power-law surface density profiles ({\bf b}; equation~\ref{eqn:sigma}) and for different mass bodies ({\bf c}).
% MAK equation reference commented out to test bug in SYW build on the github repo
{\bf b,c},The change in excess flux owing to a post-impact body with time for a simple model of cooling of a post-impact body for different power-law surface density profiles ({\bf b}) and for different mass bodies ({\bf c}).
%
Each example had an initial radius of 7\,$R_\odot$, a radiative temperature of 1000~K, and a corresponding initial flux of 0.04\,$L_\star$, as estimated for the observed infrared emitter.
%
The solid lines are profiles that can have non-zero initial density at the initial emitting radius, and the dashed lines are for ones that are forced to have zero density at the initial emitting radius.
%
When not stated, the mass of the post-impact body was 50~$M_{\rm Earth}$, the power law exponent is $-2$, and the size of the central region was 10~$R_{\rm Earth}$.
}
\label{fig:Hill_Bondi_R}
\script{plot_hill_bondi_radii_three_panels.py}

\end{centering}
\end{figure}

@@

\begin{figure}[h!]
    \centering
\includegraphics[width=0.8\textwidth]{figures/sed.pdf}
    \caption{\textbf{Spectrum of \asas{}~components.}
    %
    The red symbols show the optical and pre-brightnening WISE infrared photometry and the blue symbols show the post-brightnening WISE and ALMA fluxes.
    %
    Stellar and 1000\,K components consistent with the pre- and post-brightening fluxes are shown.
    %
    The dashed line shows an estimated cool component spectrum for $0.1\mu m$-sized grains associated with the transiting dust cloud.
    %
    Downward triangles are upper limits.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \label{fig:sed}
   \script{fvsr.py}
\end{figure}
%

@@

\begin{figure}
   \begin{centering}
\includegraphics[width=\textwidth]{figures/tess_asas_ls_epochs.pdf}
      \caption{\textbf{The light curve of ASASSN-21qj from TESS and the periodogram of TESS and ASAS-SN photometry.}
      %
      {\bf a,b},Photometry of ASASSN-21qj from three sectors of TESS.
      %
      {\bf c},Lomb-Scargle analysis of photometry from TESS (colored blue) and from ASAS-SN V band data from MJD 57420 to MJD 58386 (light grey) shows a signal at 4.4 days.
      %
      At lower frequencies, the ground based photometry shows power and aliasing signals.
      %
      The TESS signal shows a significant signal at 4.43 days, and a similar signal is seen in the ground-based data.
      %
      The longer time baseline in the ASAS-SN data reveals substructure in the signal.}
        \label{fig:TESS_lc}
        \script{plot_tess_asas_ls_epochs.py}
    \end{centering}
\end{figure}

@@

\begin{figure}
    \centering
\includegraphics[width=1\textwidth]{figures/blueing.pdf}
    \caption{\textbf{Blueing of the $B-V$ color during dimming.}
    %
    Points show AAVSO data, and lines show models.
    %
    {\bf a},The $V$ magnitude versus $B-V$ color and {\bf b}, the  $V$ magnitude versus $V-I$ color.
    %
    The dashed line is a line of $A_\lambda/A_V$ for the value shown in the legend and the solid line is a model that includes an underlying scattered-light component with $s=7.5$\% of the stellar flux.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \label{fig:blueing}
    \script{blueing.py}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/all_phot_nature_delta_flux.pdf}
\caption{\textbf{Optical and infrared photometry of ASASSN-21qj.}
%
{\bf a}, Normalized optical photometry from ASAS-SN in the $V$-band and the $g'$ band.
%
{\bf b},Fractional flux increase in brightness of ASASSN-21qj in both the $W1$ and $W2$ bands, for which a value of 1.0 represents the stellar contribution alone.
%
{\bf c},Calculated NEOWISE color temperature estimated from the photometry of the two bands.
%
The color temperature is plotted as zero when there is no infrared excess and is consistent with a temperature of 1000\,K while the excess is present.
%
Error bars are shown at $1\sigma$ confidence.
}
\script{plot_all_phot_nature_delta_flux.py}
\label{fig:wisephot}
\end{figure}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_simple.pdf}
      \caption{\textbf{The light curve of ASASSN-21qj from several different photometric surveys and the derived transverse velocities.}
      %
      {\bf a},The eclipse depth is deeper for shorter wavelengths, indicating that the transiting material is dominated by sub-micron sized grains.
      %
      {\bf b},Transverse velocities derived from the light-curve gradients.
      %
      These are lower limits to the true velocity, and thus imply that the transiting material is closer to the star than 16\,au.
      %
      Error bars are shown at $1\sigma$ confidence.
      }
\script{plot_master_lightcurve_nature_simple.py}
        \label{fig:eclipse_overview}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/Size_cooling_combined_figure.pdf}\caption{\textbf{The size and temporal evolution of a post-impact body.}
%
A post-impact body of a few to tens of Earth masses could be large enough to explain the observed increase in thermal emission from ASASSN-21qj and the subsequent infrared fluxes.
%
{\bf a},The Hill radii for bodies at different semi-major axes (solid colored lines) and the Bondi radii (dashed lines) assuming different compositions for the vapor of the post-impact body.
%
The horizontal black dashed line shows the radius required to explain the observed flux at the inferred emission temperature of 1000~K. 
%
%{\bf b,c},The change in excess flux owing to a post-impact body with time for a simple model of cooling of a post-impact body for different power-law surface density profiles ({\bf b}; equation~\ref{eqn:sigma}) and for different mass bodies ({\bf c}).
% MAK equation reference commented out to test bug in SYW build on the github repo
{\bf b,c},The change in excess flux owing to a post-impact body with time for a simple model of cooling of a post-impact body for different power-law surface density profiles ({\bf b}) and for different mass bodies ({\bf c}).
%
Each example had an initial radius of 7\,$R_\odot$, a radiative temperature of 1000~K, and a corresponding initial flux of 0.04\,$L_\star$, as estimated for the observed infrared emitter.
%
The solid lines are profiles that can have non-zero initial density at the initial emitting radius, and the dashed lines are for ones that are forced to have zero density at the initial emitting radius.
%
When not stated, the mass of the post-impact body was 50~$M_{\rm Earth}$, the power law exponent is $-2$, and the size of the central region was 10~$R_{\rm Earth}$.
}
\script{plot_hill_bondi_radii_three_panels.py}
\label{fig:Hill_Bondi_R}
\end{figure}

@@

\begin{figure}[h!]
    \centering
\includegraphics[width=0.8\textwidth]{figures/sed.pdf}
    \caption{\textbf{Spectrum of ASASSN-21qj components.}
    %
    The red symbols show the optical and pre-brightnening WISE infrared photometry and the blue symbols show the post-brightnening WISE and ALMA fluxes.
    %
    Stellar and 1000\,K components consistent with the pre- and post-brightening fluxes are shown.
    %
    The dashed line shows an estimated cool component spectrum for $0.1\mu m$-sized grains associated with the transiting dust cloud.
    %
    Downward triangles are upper limits.
    %
    Error bars are shown at $1\sigma$ confidence.
}
   \script{fvsr.py}
       \label{fig:sed}

\end{figure}
%

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/tess_asas_ls_epochs.pdf}
      \caption{\textbf{The light curve of ASASSN-21qj from TESS and the periodogram of TESS and ASAS-SN photometry.}
      %
      {\bf a,b},Photometry of ASASSN-21qj from three sectors of TESS.
      %
      {\bf c},Lomb-Scargle analysis of photometry from TESS (colored blue) and from ASAS-SN V band data from MJD 57420 to MJD 58386 (light grey) shows a signal at 4.4 days.
      %
      At lower frequencies, the ground based photometry shows power and aliasing signals.
      %
      The TESS signal shows a significant signal at 4.43 days, and a similar signal is seen in the ground-based data.
      %
      The longer time baseline in the ASAS-SN data reveals substructure in the signal.}
        \script{plot_tess_asas_ls_epochs.py}
                \label{fig:TESS_lc}

\end{figure}

@@

\begin{figure}
    \centering
\includegraphics[width=1\textwidth]{figures/blueing.pdf}
    \caption{\textbf{Blueing of the $B-V$ color during dimming.}
    %
    Points show AAVSO data, and lines show models.
    %
    {\bf a},The $V$ magnitude versus $B-V$ color and {\bf b}, the  $V$ magnitude versus $V-I$ color.
    %
    The dashed line is a line of $A_\lambda/A_V$ for the value shown in the legend and the solid line is a model that includes an underlying scattered-light component with $s=7.5$\% of the stellar flux.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \script{blueing.py}
        \label{fig:blueing}

\end{figure}
